Actuator line modeling of vertical-axis turbines

### 2016-05-13 paper.tex
Slim down conclusions

The ALM provides a more physical flow description compared to momentum and
potential flow vortex models, at a reasonable cost. The ALM also drastically
reduces computational effort compared to blade-resolved CFD, while maintaining
the unsteadiness of the wake not resolved by a conventional actuator disk.
Furthermore, its implementation within finite volume CFD provides a convenient
way to study turbine array siting, since effects like terrain and buildings can
be included, as can no-slip boundary conditions and boundary layer inflow
profiles. Since the turbinesFoam library developed here uses OpenFOAM's modular
\texttt{fvOptions} framework, the ALM body force term can be added as-is to
compressible or multiphase solvers, for exploring more complicated physics.
These features would be difficult or impossible to implement in a momentum or
vortex models.

Ultimately, the ALM retains some of the disadvantages of other blade element
methods, but is a the next logical step bridging the gap between low- and
high-fidelity flow modeling, and has been shown to be a method worthy of further
advancement. The prospect of using ALM simulations to drive down computational
cost of RANS by roughly four orders of magnitude---enabling 3-D unsteady
Navier--Stokes simulations to be performed on a typical PC---itself justifies
further development.

At contemporary levels of computing power, the ALM is a useful tool for studying
individual turbines when HPC is not feasible---requiring similar resources as
2-D blade-resolved RANS, but with improved performance predictions. Furthermore,
if arrays of CFTs advance to commercial scale, the ALM combined with LES
represents one of the highest fidelity tools available, and will improve as
turbulence modeling improves. It is therefore expected that this tool will prove
valuable for both the engineering and research of wind and MHK turbines.

>>>>

The ALM provides a more physical flow description compared to momentum and
potential flow vortex models, at a reasonable cost. The ALM also drastically
reduces computational effort compared to blade-resolved CFD, while maintaining
the unsteadiness of the wake not resolved by a conventional actuator disk. When
combined with RANS the ALM will allow VAT array simulations on individual PCs,
and with high performance computing and LES the ALM is one of the highest
fidelity array modeling tools available.
